---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```
# mapboxer

<!-- badges: start -->
[![CRAN status](https://www.r-pkg.org/badges/version/mapboxer)](https://CRAN.R-project.org/package=mapboxer)  [![Travis-CI Build Status](https://travis-ci.org/crazycapivara/mapboxer.svg?branch=master)](https://travis-ci.org/crazycapivara/mapboxer) [![Project Status: Active – The project has reached a stable, usable state and is being actively developed.](https://www.repostatus.org/badges/latest/active.svg)](https://www.repostatus.org/#active)
<!-- badges: end -->

The __mapboxer__ package makes [Mapbox GL JS](https://docs.mapbox.com/mapbox-gl-js/api/),
an open source JavaScript library that uses WebGL to render interactive maps,
available within R via the [htmlwidgets](https://www.htmlwidgets.org/) package.

## Installation

Install the development version from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("crazycapivara/mapboxer")
```

## Quickstart

```{r example, eval = FALSE}
library(mapboxer)

fill_style <- list(
  id = "melbourne",
  type = "fill",
  paint = list(
    "fill-color" = c("get", "fillColor"),
    "fill-opacity" = 0.7
  )
)

geojsonsf::geo_melbourne %>%
  as_mapbox_source() %>%
  mapboxer() %>%
  set_view_state(lng =  144.9624, lat = -37.8105, zoom = 10, pitch = 35) %>%
  add_layer(fill_style, popup = "Area: {{AREASQKM}} km<sup>2</sup>")
```

## Documentation

The package is still in an early stage, so the documention is work in progress.

[mapboxer-docs](https://crazycapivara.github.io/mapboxer/)
