---
title: "Get started with Mapbox for R"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{mapboxer}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

The goal of mapboxer is to make it easy to create interactive maps using [Mapbox GL JS](https://docs.mapbox.com/mapbox-gl-js/api) within R. Visualizations can be used at the R console, embedded in R Markdown documents or Shiny apps.

This guide covers the basic usage.

## Overview

* [Map](https://docs.mapbox.com/mapbox-gl-js/api/map/): The map is the main component of your visualization to which you then add other components like layers, controls or sources. Maps are created with `mapboxer()`.

* [Sources](https://docs.mapbox.com/mapbox-gl-js/style-spec/sources/): Sources state which type of data should be displayed on the map. R objects can be converted to Mapbox sources with `as_mapbox_source()`. With `add_source()` or as first parameter of `mapboxer()` sources can be added to the map so that they can be used accross layers.

* [Layers](https://docs.mapbox.com/mapbox-gl-js/style-spec/layers/): A layer's style define how a source is displayed on the map. Furthermore, you can apply filters to the data of a source. With `add_layer()` you can add any type of layer to the map but in most cases it is easier to use one of the shortcuts like `add_circle_layer()`.  

* [Controls](https://docs.mapbox.com/mapbox-gl-js/api/markers/): Controls are used to interact with the map. Besides the standard controls like `NavigationControl` included in Mapbox GL JS, mapboxer provides additional controls. For example, `add_filter_control()` can be used to filter your data on the fly without having to set up a Shiny app.

* [Expressions](https://docs.mapbox.com/help/tutorials/mapbox-gl-js-expressions/): Expressions are pretty powerful. Among other things, they can be used for data-driven-styling or to filter your data.

* [Shiny Bindings](https://shiny.rstudio.com/): With `renderMapboxer()` and `mapboxerOutput()` you can integrate your visualizations in Shiny apps. Furthermore, you can use `mapboxer_proxy()` and `update_mapboxer()` to update an already rendered widget. Observe the `input$<widget_id>_onclick` event to get the properties for a clicked feature.

## Quickstart

```{r quickstart, eval = FALSE}
# Load the library
library(mapboxer)

# Create a source
motor_vehicle_collisions_nyc %>%
  as_mapbox_source(lng = "lng", lat = "lat") %>%
  # Setup a map with the default source above
  mapboxer(
    center = c(-73.9165, 40.7114),
    zoom = 9
  ) %>%
  # Add a layer styling the data of the default source
  add_circle_layer(
    circle_color = "red",
    circle_radius = 5,
    # Use a mustache template to add popups to the layer
    popup = "Number of persons injured: {{injured}}"
  )
```

## Map

With `mapboxer()` you create a map object. This is the main component of your vizualization. To add components like layers or controls or to modify your map you use the `add_*` and `set_*` functions.
The options to configure your map are set via the `...` parameter that allows you to pass on any option described in the [Map API Reference](https://docs.mapbox.com/mapbox-gl-js/api/map/):

```r
mapboxer(
  style = basemaps$Carto$dark_matter,
  center = c(-73.9165, 40.7114),
  zoom = 9,
  minZoom = 8
)
```

With the optional `source` parameter you can add a default source to the map that will be used by the layers if no source is provided. Therefore, it is easy to integrate `mapboxer()` into your workflow:

```{r, eval = FALSE}
motor_vehicle_collisions_nyc %>%
  dplyr::filter(killed > 0) %>%
  as_mapbox_source() %>%
  mapboxer(
    center = c(-73.9165, 40.7114),
    zoom = 9
  ) %>%
  add_circle_layer(circle_color = "red")
```

As you can see above mapboxer is designed to use the widely used piping style provided by [magrittr](https://magrittr.tidyverse.org/).

## Basemaps

The `style` parameter passed to `mapboxer()` sets the style of the basemap. By default mapboxer uses a [Carto vector style](https://github.com/CartoDB/basemap-styles). It is also possible to use raster tiles or a background color as basemap. Therefore, you can use the helpers `basemap_raster_style()` or `basemap_background_style()`:

```r
mapboxer(style = basemap_raster_style())
```

To use styles from [Mapbox](https://www.mapbox.com/maps) it is recommened that your store your API token in an environment variable called `MAPBOX_API_TOKEN`. If not set globally you can store it as follows:

```r
Sys.setenv(MAPBOX_API_TOKEN = "<yourSuperSecretToken>")

mapboxer(style = basemaps$Mapbox$satellite_v9)
```

## Sources

Sources state which data the map should display. To show the data on the map you need
to bind a source to a layer which contains the styling details like color or width. 
This makes it possible to style the same source in different ways.
The easiest way to create a source from an R data object is to use `as_mapbox_source()`.
Supported structures are [sf](https://r-spatial.github.io/sf/index.html)-objects and data frames that contain longitudes and latitudes:

```{r, eval = FALSE}
mvc_sf <- motor_vehicle_collisions_nyc %>%
  sf::st_as_sf(coords = c("lng", "lat"), crs = 4326)

mvc_source_from_sf <- mvc_sf %>%
  as_mapbox_source()

mvc_source_from_df <- motor_vehicle_collisions_nyc %>%
  as_mapbox_source(lng = "lng", lat = "lat")
```

With the `...` parameter you can pass additional options to the source:

```r
mvc_cluster <- motor_vehicle_collisions_nyc %>%
  as_mapbox_source(
    lat = "lat",
    lng = "lng",
    cluster = TRUE,
    clusterMaxZoom = 14,
    clusterRadius = 50
  )
```

See the [Sources API Reference](https://docs.mapbox.com/mapbox-gl-js/style-spec/sources/) for available options for the used source type. Sources are either passed to the `add_*_layer` functions or as first parameter to `mapboxer()` setting it as default source. With `add_source()` you can add a source to the map that you refer to in the layer definition by its ID.

## Layers

Layers style the data of the source to which they refer. Optionally you can filter features. Each layer must have a unique ID. If you use the generic function `add_layer()`, the type of the layer is specified by the `type` property. See the [Layers API Reference](https://docs.mapbox.com/mapbox-gl-js/style-spec/layers/) for available types. In most cases it is convenient to use one of the `add_*_layer()` functions:

```{r, eval = FALSE}
mapboxer(
  center = c(-73.9165, 40.7114),
  zoom = 9
) %>%
  add_circle_layer(
    source = as_mapbox_source(motor_vehicle_collisions_nyc),
    circle_color = "red",
    circle_radius = 5
  )
```

## Popups and tooltips

Usually popups are added to a layer with the `popup` parameter of the `add_*_layer()` functions. Optionally you can also use `add_popups()`. The popup text (HTML) is specified by a [mustache](https://github.com/janl/mustache.js) template in which the tags refer to the properties of the layer's data object. If your data contains the properties `name` and `population`, it could look like this:

```r
popup_template <- "Name: {{name}}</br>Population: {{population}}"
```

With `add_tooltips()` you can add tooltips to a layer in the same way.

## Controls

Controls are used to interact with the user. They are displayed as overlays on top of the map. Options of the standard controls described in the [Markers and Controls API Reference](https://docs.mapbox.com/mapbox-gl-js/api/markers/) are provided with the
`...` parameter. The position is set with the `pos` parameter, one of `top-left`, `top-right`, `bottom-right`, `bottom-left`:

```{r, eval = FALSE}
mapboxer() %>%
  add_navigation_control(
    pos = "top-left",
    # Option passed to the 'NavigationControl'
    showCompass = FALSE
) %>%
  add_scale_control(
    pos = "bottom-left",
    # Option passed to the 'ScaleControl'
    unit = "nautical"
) %>%
  add_text_control(
    pos = "top-right",
    text = "mapboxer"
  )
```

## Expressions

The value of any layout property, paint property (data-driven-styling) or filter may be specified as an expression. Expressions in Mapbox GL JS use a Lisp-like [syntax](https://docs.mapbox.com/help/tutorials/mapbox-gl-js-expressions/#syntax) represented as JSON arrays:

```javascript
[expression_name, argument_0, argument_1, ...]
```

Therefore, in R you must use the `list` structure:

```r
list(expression_name, argument_0, argument_1, ...)
```

If all elements are of the same type you can also use a vector:
```r
expr_get_property <- c("get", "<data-property>")`
```

A simple expression is to use a data property to style your data:

```{r, eval = FALSE}
map <- motor_vehicle_collisions_nyc %>%
  dplyr::mutate(
    color = ifelse(injured > 0, "red", "yellow")
  ) %>%
  as_mapbox_source() %>%
  mapboxer(
    center = c(-73.9165, 40.7114),
    zoom = 9
  )
  
map %>%
  add_circle_layer(
    # Expression to get the color from the data's color property
    circle_color = c("get", "color")
  )
```

You can get the same result for the `circle_color` without modifying the data but using
expressions only:

```{r, eval = FALSE}
map %>%
  add_circle_layer(
    circle_color = list(
      "case",
      # 'red' if 'injured > 0'
      list(">", c("get", "injured"), 0), "red",
      # Defaults to 'yellow'
      "yellow"
    )
  )
```

A filter could look like this:

```{r, eval = FALSE}
map %>%
  add_circle_layer(
    circle_color = c("get", "color"),
    # Expression to display only data where 'injured > 1'
    filter = list(">", "injured", 1)
  )
```

See also `add_filter_control()` to modify filter expressions on the fly to update your map without the need of a Shiny app, [Get started with expressions](https://docs.mapbox.com/help/tutorials/mapbox-gl-js-expressions/) for a tutorial and the [Expressions Style Specification](https://docs.mapbox.com/mapbox-gl-js/style-spec/expressions/) for details.

## Shiny Bindings

Use `mapboxerOutput()` and `renderMapboxer()` to integrate mapboxer in a [Shiny](https://shiny.rstudio.com/) app:

```{r, eval = FALSE}
library(shiny)
library(mapboxer)

view <- fluidPage(
  h1("mapboxer"),
  mapboxerOutput("map")
)

backend <- function(input, output) {
  output$map <- renderMapboxer({
    mapboxer(center = c(9.5, 51.3), zoom = 10) %>%
      add_navigation_control() %>%
      add_marker(lng = 9.5, lat = 51.3, popup = "mapboxer")
  })
}

if (interactive()) shinyApp(view, backend)
```

With `mapboxer_proxy()` and `update_mapboxer()` you can update your already rendered map:

```{r, eval = FALSE}
LAYER_ID <- "crashes"
START_VALUE <- 4

view <- basicPage(
  sliderInput("slider", "Number of persons injured:",
              min = 0, max = 7, step = 1, value = START_VALUE),
  mapboxerOutput("map")
)

backend <- function(input, output) {
  output$map <- renderMapboxer({
    mapboxer(
      center = c(-73.9165, 40.7114),
      zoom = 9
    ) %>%
      add_circle_layer(
        source = as_mapbox_source(motor_vehicle_collisions_nyc),
        circle_color = "red",
        popup = "{{injured}}",
        filter = list("==", "injured", START_VALUE),
        id = LAYER_ID
      )
  })

  observeEvent(input$slider, {
    mapboxer_proxy("map") %>%
      set_filter(LAYER_ID, list("==", "injured", input$slider)) %>%
      update_mapboxer()
  })
}

if (interactive()) shinyApp(view, backend)
```

Observe the `input$<widget_id>_onclick` event to get the properties for a clicked feature.
