---
title: Showcase
---

The examples below show Motor Vehicle Collisions in NYC.

## Unclustered

```{r}
library(mapboxer)

LAYER_ID <- "crashes"

mvc <- motor_vehicle_collisions_nyc
mvc$color <- cut(
  mvc$injured,
  breaks = c(0, 1, 2, Inf),
  labels = c("yellow", "orange", "red"),
  right = FALSE
) %>% as.character()

map <- as_mapbox_source(mvc) %>%
  mapboxer(
    center = c(-73.9165, 40.7114),
    zoom = 10
  ) %>%
  add_navigation_control() %>%
  add_circle_layer(
    id = LAYER_ID,
    circle_color = c("get", "color"),
    popup = "<p>{{date}} {{time}}</p><p>Number of injured persons: {{injured}}</p>"
  ) %>%
  add_filter_control(
    LAYER_ID,
    filter = list(">=", "injured", 0),
    pos = "top-left"
  )

map
```

Use the textbox on the map to filter your data.

## Clustered

Point features can be clustered into groups by setting `cluster = TRUE` in your source definition. Clustered points have the additional properties `point_count` and `point_count_abbreviated` that can be used in expressions and popups. See [Mapbox Sources API Reference](https://docs.mapbox.com/mapbox-gl-js/style-spec/sources/#geojson) for more details.

```{r}
map <- as_mapbox_source(
  mvc,
  cluster = TRUE,
  clusterMaxZoom = 11,
  clusterRadius = 50
) %>%
  mapboxer(
    center = c(-73.9165, 40.7114),
    zoom = 10,
    minZoom = 9
  ) %>%
  add_navigation_control() %>%
  add_circle_layer(
    id = "clustered",
    circle_color = "blue",
    circle_radius = list(
      "step", c("get", "point_count"),
      10, 40,
      15, 60,
      20, 80,
      25, 100,
      30
    ),
    popup = "{{point_count}}",
    filter = c("has", "point_count")
  ) %>%
  add_circle_layer(
    id = "unclustered",
    filter = list("!", c("has", "point_count")),
    circle_color = "red",
    circle_radius = 5,
    popup = "{{date}} {{time}}"
  )

map
```
