---
title: Showcase
---

The examples below show Motor Vehicle Collisions in NYC.

## Point Layer

```{r}
library(mapboxer)

LAYER_ID <- "crashes"

mvc <- motor_vehicle_collisions_nyc
mvc$color <- cut(
  mvc$injured,
  breaks = c(0, 1, 2, Inf),
  labels = c("yellow", "orange", "red"),
  right = FALSE
) %>% as.character()

map <- as_mapbox_source(mvc) %>%
  mapboxer(
    center = c(-73.9165, 40.7114),
    zoom = 10
  ) %>%
  add_navigation_control() %>%
  add_circle_layer(
    id = LAYER_ID,
    circle_color = c("get", "color"),
    popup = "<p>{{date}} {{time}}</p><p>Number of persons injured: {{injured}}</p>"
  ) %>%
  add_filter_control(
    LAYER_ID,
    filter = list(">=", "injured", 0),
    pos = "top-left"
  )

map
```

Use the textbox on the map to filter your data.

## Clustered Point Layer

Point features can be clustered into groups by setting `cluster = TRUE` in your source definition. Clustered points have the additional properties `point_count` and `point_count_abbreviated` that can be used in expressions and popups. See [Mapbox Sources API Reference](https://docs.mapbox.com/mapbox-gl-js/style-spec/sources/#geojson) for more details.

```{r}
map <- as_mapbox_source(
  mvc,
  cluster = TRUE,
  clusterMaxZoom = 11,
  clusterRadius = 50,
  clusterProperties = list(
    sumInjured = list("+", c("get", "injured"))
  )
) %>%
  mapboxer(
    center = c(-73.9165, 40.7114),
    zoom = 10,
    minZoom = 9
  ) %>%
  add_navigation_control() %>%
  add_circle_layer(
    id = "clustered",
    circle_color = "blue",
    circle_radius = list(
      "step", c("get", "point_count"),
      10, 40, # 10px if point count < 40
      15, 60, # 15px if point count >= 40 and < 60
      20, 80, # 20px if point count >= 60 and < 80
      25, 100, # 25px if point count >= 80 and < 100
      30 # 30px if point count >= 100
    ),
    popup = "Number of crashes: {{point_count}}, Number of persons injured: {{sumInjured}}",
    filter = c("has", "point_count")
  ) %>%
  add_circle_layer(
    id = "unclustered",
    filter = list("!", c("has", "point_count")),
    circle_color = "red",
    circle_radius = 5,
    popup = "{{date}} {{time}}"
  )

map
```

## Filled Polygon Layer

```{r}
mvc_sf <- sf::st_as_sf(
  motor_vehicle_collisions_nyc,
  coords = c("lng", "lat"),
  crs = 4326
)

sf::sf_use_s2(TRUE)

grid_sf <- sf::st_make_grid(mvc_sf, square = TRUE)[mvc_sf] %>%
  sf::st_sf()

grid_sf <- dplyr::mutate(
  grid_sf,
  count = lengths(sf::st_intersects(grid_sf, mvc_sf)),
  color = scales::col_quantile("Blues", count)(count)
)

map <- as_mapbox_source(grid_sf) %>%
  mapboxer(
    bounds = unname(sf::st_bbox(grid_sf)),
    fitBoundsOptions = list(padding = 20)
  ) %>%
  add_navigation_control() %>%
  add_fill_layer(
    fill_color = c("get", "color"),
    fill_antialias = FALSE,
    fill_opacity = 0.4,
    popup = "Number of crashes: {{count}}"
  )

map
```
